---
title: "hw9"
output:
  pdf_document: default
  html_document: default
date: "2024-04-12"
---

# 3a

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
```

```{r}
yX<-dget(url("http://www2.stat.duke.edu/~pdh10/FCBS/Inline/yX.diabetes.train"))
```

```{r}
X <- yX[,-1]
y <- yX[,1]

BETA.l = NULL

for (l in 0:100){
  XTX = t(X)%*%X
  Il = diag(l, ncol(X))
  XTy = t(X)%*%y
  beta.l = solve(XTX + Il)%*%XTy
  BETA.l = cbind(BETA.l, beta.l)
}

df = as.data.frame(t(BETA.l))%>%
  mutate(l = 0:100)
  
df.plot <- df %>%
  pivot_longer(cols=1:64)

png("3a_plot.png", width = 1200, height = 800)

p <- ggplot(data = df.plot, aes(x=l))+
  geom_point(aes(y=value))+
  facet_wrap(~name)+
  ylim(c(-.5,.5))

print(p)

dev.off()
```

# 3b

```{r}
yX.test<-dget(url("http://www2.stat.duke.edu/~pdh10/FCBS/Inline/yX.diabetes.test"))
```

```{r}
X.test <- yX.test[,-1]
y.test <- yX.test[,1]

y.pred <- NULL
PSS <- NULL

for (l in 0:100){
  y.pred = X.test%*%BETA.l[,l+1]
  PSS = cbind(PSS, sum((y.test-y.pred)^2))
}

df = as.data.frame(t(PSS))%>%
  mutate(l = 0:100)

ggplot(data=df, aes(x=l, y=V1))+
  geom_point()
```

As we can see, the PSS for when $\lambda$=0 (OLS estimate) is about 67. We see a drastic drop in PSS from $\lambda$=0 to $\lambda$=1, and even more of a decline moving forward (PSS seems to reach a minimum at around $\lambda$=60). Moreover the OLS estimator has higher PSS than all of the other estimates.

# 3c

```{r}
min(df$V1)
df$l[which(df$V1==min(df$V1))]
```

Of the lambda values, the PSS is lowest at 53.13 when lambda is 64.

```{r}
sort(BETA.l[,65])
```
The most important predictors when lambda is 64 are bmi, ltg, map, hdl, and sex.

# 4a

```{r}

```



